Trends of SDR in Thessaloniki

### 2023-09-15 Article.Rmd
Commit 2023-09-15 17:10

## some vars to use later
alltrend   <- signif(LT[`Sky condition` == "All sky cond.",   `Trend [%/year]`], 2)
cleartrend <- signif(LT[`Sky condition` == "Clear sky cond.", `Trend [%/year]`], 2)
cloudtrend <- signif(LT[`Sky condition` == "Cloudy cond.",    `Trend [%/year]`], 2)

@@

The solar zenith angle  is a major driver of the attenuation of SDR reaching the ground, as SDR is affected by the enhancement of the radiation path in the atmosphere, especially in urban environment with human activities emitting aerosols [@Wang2021].
In order to estimate the effect of the SZA on the SDR trends, we grouped the anomaly data in bin of $1^\circ$ SZA, and calculated the overall trend for each bin before noon and after noon (Figure\ \ref{fig:szatrends}).
Although there is a seasonal variation of the minimum SZA, that is not examined here.
The brightening effect of SDR is stronger for all-sky and clear-sky condition for low Sun elevation angles (Figures\ \ref{fig:szatrends}a and \ref{fig:szatrends}b).
In the case of cloud-sky condition (Figure\ \ref{fig:szatrends}c), there is no strong correlation between SDR brightening and SZA, except for some low Sun angles, that occur only for a small part of the year, and thus we can not draw more conclusions from this analysis for the overall trends.

@@

\newpage
# Appendix

>>>>

## some vars to use later
alltrend   <- signif(LT[`Sky condition` == "All sky cond.",    `Trend [%/year]`], 2)
cleartrend <- signif(LT[`Sky condition` == "Clear sky cond.",  `Trend [%/year]`], 2)
cloudtrend <- signif(LT[`Sky condition` == "Cloudy sky cond.", `Trend [%/year]`], 2)

@@

The solar zenith angle  is a major driver of the attenuation of SDR reaching the ground, as SDR is affected by the enhancement of the radiation path in the atmosphere, especially in urban environment with human activities emitting aerosols [@Wang2021].
In order to estimate the effect of the SZA on the SDR trends, we grouped the anomaly data in bin of $1^\circ$ SZA, and calculated the overall trend for each bin before noon and after noon (Figure\ \ref{fig:szatrends}).
Although there is a seasonal variation of the minimum SZA, its possible effect has not been examined here.
The brightening effect of SDR is stronger for all-sky and clear-sky condition for low Sun elevation angles (Figures\ \ref{fig:szatrends}a and \ref{fig:szatrends}b).
In the case of cloud-sky condition (Figure\ \ref{fig:szatrends}c), there is no strong correlation between SDR brightening and SZA, except for some low Sun angles, that occur only for a small part of the year, and thus we can not draw more conclusions from this analysis for the overall trends.

@@

# Appendix
